Community Embeddings for Friend Suggestions

### 2020-10-12 conference_101719.tex
write some embedding FFS
add embedding stuff from MT

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{subcaption}
\usepackage[style=numeric, backend=bibtex, language=english, maxbibnames=99]{biblatex}

@@

>>>>

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{subcaption}
\usepackage[super]{nth}
\usepackage[style=numeric, backend=bibtex, language=english, maxbibnames=99]{biblatex}

@@

Community embeddings for the \citetitle{social_circles_fb} graph are generated by running ComE BGMM+VI with the hyperparameters listed in Table \ref{tab:params_fb}.

\begin{table}
    \centering
    \caption{Hyperparameters used for the \citetitle{social_circles_fb} dataset.}
    \label{tab:params_fb}
    \begin{tabular}{ l | c | r }
        parameter                    & notation & value       \\
        \hline
        \hline
        number\_walks                & $\gamma$ & $10$        \\
        \hline
        walk\_length                 & $\ell$   & $80$        \\
        \hline
        representation\_size         & $D$      & $2, 4, 128$ \\
        \hline
        num\_workers                 & \empty   & $10$        \\
        \hline
        num\_iter                    & \empty   & $3$         \\
        \hline
        com\_n\_init                 & \empty   & $10$        \\
        \hline
        reg\_covar                   & \empty   & $0.00001$   \\
        \hline
        batch\_size                  & \empty   & $50$        \\
        \hline
        window\_size                 & $\zeta$  & $10$        \\
        \hline
        negative                     & $m$      & $5$         \\
        \hline
        lr                           & \empty   & $0.025$     \\
        \hline
        alpha                        & $\alpha$ & $0.1$       \\
        \hline
        beta                         & $\beta$  & $0.1$       \\
        \hline
        down\_sampling               & \empty   & $0.0$       \\
        \hline
        communities                  & $K$      & $10$        \\
        \hline
        weight\_concentration\_prior & $\Gamma$ & $10^{-5}$   \\
    \end{tabular}
\end{table}

As is shown in Table \ref{tab:params_fb}, the embedding's representation size $D$ is varied along three values. A representation size $D \in [2,4,128]$ is chosen to determine the effect of the embedding's dimensionality on friend suggestions. It is hypothesized, that two dimensions are not sufficient to capture the structure of the \citetitle{social_circles_fb} graph, due to its size, therefore higher dimensional embeddings are evaluated as well.

Fig. \ref{fig:fb_emb_anim_d2}, Fig. \ref{fig:fb_emb_anim_d4}, and Fig. \ref{fig:fb_emb_anim_d128} show the node embeddings generated by ComE BGMM+VI after one, two, and three iterations. The nodes are colored by community membership from ComE's community embedding and detection.
The $4$- and $128$-dimensional node and community embeddings cannot effectively be plotted in two-dimensional print. Instead, in Figures \ref{fig:fb_emb_anim_d4} and \ref{fig:fb_emb_anim_d128} the two first dimensions of the node and community embeddings are plotted to gain a narrow perspective on the resulting node embeddings.

\newcommand{\fbEmbAnimD}[1]{
    \begin{figure*}
        \centering
        \begin{subfigure}{.33\textwidth}
            \centering
            \includegraphics[width=1\linewidth]{images/fb/anim_d#1_i0.png}
            \caption{\nth{1} Iteration \\$D=#1$.}
        \end{subfigure}%
        %
        \begin{subfigure}{.33\textwidth}
            \centering
            \includegraphics[width=1\linewidth]{images/fb/anim_d#1_i1.png}
            \caption{\nth{2} Iteration\\$D=#1$}
        \end{subfigure}%
        %
        \begin{subfigure}{.33\textwidth}
            \centering
            \includegraphics[width=1\linewidth]{images/fb/anim_d#1_i2.png}
            \caption{\nth{3} Iteration\\$D=#1$}
        \end{subfigure}%
        %
        \caption{Node embeddings segment with representation size $D=#1$.}
        \label{fig:fb_emb_anim_d#1}
    \end{figure*}
}

\fbEmbAnimD{2}
\fbEmbAnimD{4}
\fbEmbAnimD{128}

Fig. \ref{fig:fb_graphs} shows the graph spring plotted with networkx and nodes colored by community membership after the lastest iteration of ComE.\cite{networkx} The spring plotted graph structure on Figure \ref{fig:fb_graphs} suggest, that with embedding dimension $D=4$, more fitting communities are detected than for $D=2$ and $D=128$.

\begin{figure*}
    \centering
    \begin{subfigure}{.33\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{images/fb/graph_d2.png}
        \caption{$D=2$}
    \end{subfigure}%
    %
    \begin{subfigure}{.33\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{images/fb/graph_d4.png}
        \caption{$D=4$}
    \end{subfigure}%
    %
    \begin{subfigure}{.33\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{images/fb/graph_d128.png}
        \caption{$D=128$}
    \end{subfigure}%
    %
    \caption{Spring plotted graphs with nodes colored by community membership after last ComE BGMM+VI iteration.}
    \label{fig:fb_graphs}
\end{figure*}

Figure \ref{fig:fb_emb_anim_d2} shows node and community embeddings with representation size $D=2$. The limiting two-dimensional space does not allow ComE to represent the \citetitle{social_circles_fb} graph's structure sufficiently to utilize the $K=10$ components of the Gaussian mixture model. Only three components are used after the last of three iterations.

While Figures \ref{fig:fb_emb_anim_d4} and \ref{fig:fb_emb_anim_d128} show only the first two dimensions, of the node embedding of 4 or 128 dimensionality respectively, the general structure of communities is visible. The development of the node embeddings over the three iterations shows the manifestation of the first-, second-, and higher-order proximity by ComE's closed loop. The node embeddings are densified in their communities and spread out in regards to other communities. All $K=10$ components of the Gaussian mixture model are used for $D=4$ and $D=128$.

Node are distributed over the $K=10$ communities as shown in the histogram in Figure \ref{fig:fb_emb_weights}:

\begin{figure*}
    \centering
    %
    \begin{subfigure}{.33\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{images/fb/weights_d2.png}
        \caption{$D=2$}
        \label{fig:fb_emb_weights_d2}
    \end{subfigure}%
    %
    \begin{subfigure}{.33\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{images/fb/weights_d4.png}
        \caption{$D=4$}
        \label{fig:fb_emb_weights_d4}
    \end{subfigure}%
    %
    \begin{subfigure}{.33\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{images/fb/weights_d128.png}
        \caption{$D=128$}
        \label{fig:fb_emb_weights_d128}
    \end{subfigure}%
    %
    \caption{Weights of communities with $K=10$ and $D \in [2,4,128]$.}
    \label{fig:fb_emb_weights}
\end{figure*}

Figure \ref{fig:fb_emb_weights_d2} shows that with representation size $D=2$, ComE BGMM+VI drops 6 communites, effecitvelly using only 4 communities in the final embedding, because the two-dimensional node embeddings are not expressive enough to support more communities. Figures \ref{fig:fb_emb_weights_d4} and \ref{fig:fb_emb_weights_d128} show that with representation sizes $D=4$ and $D=128$ respectivelly, all $K=10$ communities are used.
